---
title: "p8105_hw1_yl5220"
output: github_document
date: "2022-09-24"
---

# Problem 1

**Import dataset**
```{r}
library(tidyverse)
data("penguins", package = "palmerpenguins")
```

**Clean NA values from the dataset**
```{r}
penguins = drop_na(penguins)
```

**Description of dataset**
The names and values of important variables are `r colnames(penguins)`
The size of the dataset is: `r nrow(penguins)` rows and `r ncol(penguins)` columns
The mean flipper length is: `r mean(penguins$flipper_length_mm)` mm

**Make scatterplot**
```{r}
ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, color = species)) + geom_point()
ggsave("penguins.pdf")
```

# Problem 2

**Create dataframe**
```{r}
example_df = tibble(
  sample = rnorm(10),
  vec_logical = sample > 0,
  vec_char = c("My", "name", "is", "Yixuan", "Hi", "again", "this", "is", "Yichen", "bye"),
  vec_factor = factor(c("male", "male", "male", "female", "female", "female", "other", "other", "other", "other"))
)
```

**Take the mean of each variable**
```{r}
mean(example_df$sample)
mean(example_df$vec_logical)
mean(example_df$vec_char)
mean(example_df$vec_factor)
```
Mean works for the numeric and logistic type, but not for the character and factor types. 

**Apply as.numeric function**
```{r}
as.numeric(example_df$sample)
as.numeric(example_df$vec_logical)
as.numeric(example_df$vec_char)
as.numeric(example_df$vec_factor)
```
The function turned logical type into values 0 and 1, factor type into number series, and character type into NA. This helps explain why the mean of logistic type can be taken.